Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
horz lines in Fig 5
reformulate EMD section VI

\gl{vincent, un petit mot pour motiver le fait que le scattering est un bon outil pour separer les evenements peuplant une scène sonore ?}. 
\vl{this section should be better segmented into subsections. The words centroid and cluster are defined after they are used. The order of paragraphs could be 1-4-3-2-5.}

As discussed in Section \ref{sec:motivations}, results in sound perception suggest the appropriateness of an object-based representation of auditory scenes for predicting high-level properties. That being said, perfect knowledge of which event occurred at a given time is not feasible. \ja{What does this mean?} In this paper, we therefore focus on a simple quantization scheme that is as generic as possible, implemented using a clustering approach where coherent regions of the scene are identified.

\ja{We need to describe the clustering here and what it gives as output. Otherwise it becomes difficult to describe the way we compare scenes below.}

One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, which clusters not over a single scene, but over the whole dataset, and re-projects each scene in the resulting enhanced feature space. \ja{This sentence is also a big unclear.}
Here, with the aim of better balancing the influence of salient sound events and texture-like sounds on the final decision, we consider several centroid-based similarity metrics:

\begin{itemize}
\item \emph{ob-closest} (ob-c): the similarity between two scenes is equal to the largest similarity between their centroids,
\item \emph{ob-averaged} (ob-a): the similarity between two scenes is equal to the average of their centroids similarities, and
\item \emph{ob-weighted} (ob-w): for each scene, each centroid is weighted according to the number of frames belonging to its cluster. \ja{And then we compute the EMD?}
\end{itemize}

The similarity between two centroids $c_i$ and $c_j$ is computed using a radial basis function (RBF) kernel $K^c$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K^c_{ij} = \exp\left( - \dfrac{\Vert c_i - c_j \Vert^2}{\Vert c_i - c_N \Vert \Vert c_j - c_N \Vert} \right) 
\end{equation} \ja{To simplify the analysis later, can we already specify that we're looking at a specific pair $(u, v)$ and that the kernel $K^c$ is defined only for $i$ in $u$ and $j$ in $v$?}
where $c_N$ is the $N^{\textrm{th}}$ nearest neighbor to the centroid $c_i$, and $\Vert \cdot \Vert$ denotes the Euclidean norm. \ja{How does the $c_N$ notation distinguish between $c_i$ and $c_j$? Do we have $c_{i,N}$ and $c_{j,N}$?}

Compared to the closest or averaged approach, the weighted similarity between two scenes takes into account both the centroids similarities and the clusters weights. Each scene $s_u$ is described by a signature $S_u$ of $m$ clusters ($S_u=\lbrace(c_1^u,w_1^u),\ldots,(c_m^u,w_m^u)\rbrace$), with $c_i^u$ and $w_i^u$ being the centroid and the weight of the $i$th cluster of the scene $s_u$ respectively. \ja{Everything that follows only refers to the ob-w metric, correct? If so, we should specify it here, and also say how the similarity is explicitly calculated for the other options}

To compute the distance between two signatures $S_u$ and $S_v$, we use a variant of the earth mover's distance ($\EMD$), known as $\widehat{\EMD}$ and introduced in \cite{pele2008linear}. The $\EMD$ distance is a cross-bin histogram distance, widely used in computer vision \cite{zhang2007local}, which computes the minimal cost to be paid to transform one histogram into the other. An advantage of $\EMD$ is that automatically aligns the histogram bins by using a ``ground distance,'' which is the distance between the bin centers in the two histograms. In our case, the histograms are the cluster weights $w$ defined over the bins formed by cluster centroids $c$.

The $\widehat{\EMD}$ variant of $\EMD$ is adapted for non-normalized histograms. To compute the $\widehat{\EMD}$, we use the implementation proposed in \cite{pele2009fast}. Given two signatures $S_u$ and $S_v$, the $\widehat{EMD}$ is computed by solving the following linear programming problem:

\begin{equation}
\begin{split}
\widehat{\EMD}(S_u,S_v) &=\left( \min\limits_{\lbrace f_{ij}\rbrace} \sum\limits_{i,j} f_{ij}D_{ij} \right) \\
&+ \left|\sum\limits_{i} w_i^u - \sum\limits_{j} w_j^v  \right| \alpha \max\limits_{i,j}\lbrace  D_{ij}\rbrace
\end{split}
\end{equation}

\begin{equation*}
\mathrm{s.t.} \quad f_{ij}\geq0 \quad \sum\limits_{j} f_{ij} \leq w_i^u \quad \sum\limits_{i} f_{ij} \leq w_j^v
\end{equation*}

\begin{equation*}
\sum\limits_{i,j}f_{ij} = \min\left( \sum\limits_{i} w_i^u ,\sum\limits_{j} w_j^v \right)
\end{equation*} \ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{ij} \rbrace$ is the flow between the cluster weights $w_i^u$ and $w_j^v$, that is, the amount transported from the $i$th bin to ``supply the demand'' of the $j$th bin. We denote by $D_{ij}$ the ground distance between the centroids $c_i^u$ and $c_j^v$ computed from the kernel $K^c$:
\begin{equation*}
D_{ij}=1-K^{c(uv)}_{ij}
\end{equation*}
with $K^{c(uv)}$ being the slice of $K^{c}$ containing the pairwise similarities between the centroids sets $c^u$ and $c^v$ of the scenes $s_u$ and $s_v$ respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

To get the final similarity measure between the scenes $s_u$ and $s_v$, an extended Gaussian kernels $K^s$ \cite{chapelle1999support,jing2003support} is computed:
\begin{equation}
\label{eq:ks}
K_{uv}^s = \exp\left( - \dfrac{\widehat{\EMD}(S_u,S_v)}{A} \right) \\
\end{equation}
with $A$ a scaling parameter, set to the mean value of the $\widehat{\EMD}$ between all the scenes. The resulting kernel $K^s$ is known as an EMD kernel, and it should be noted that there is no guarantee that this kernel is positive definite.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.
See text for details.\ml{je mettrai des lignes fines entre les points 1 et 3, et 4 et 6, je zoomerai un peu et l'axe des y n'est pas numerote ni labelise }}
\end{center}
\ref{fig:folds}
\end{figure}

>>>>

As discussed in Section \ref{sec:motivations}, results in sound perception suggest the appropriateness of an object-based representation of auditory scenes for predicting high-level properties. That being said, perfect knowledge of which event occurred at a given time is not feasible. \ja{What does this mean?} In this paper, we therefore focus on a simple quantization scheme that is as generic as possible, implemented using a clustering approach where coherent regions of the scene are identified. The clustering is done using the centroid-based clustering algorithm KMeans.

Given a set a $d$-dimensional feature vectors $x_l^u\in X_u$, $l=[1,2,\ldots,L]$, extracted from the scene $s_u$, $u=[1,2,\ldots,U]$, the goal of KMeans is to partition $X_u$ into $M$ clusters $c^u_m\in C_u$, $m=[1,2,\ldots,M]$. The partitioning is done by minimizing for each $m$ cluster the squared error between its empirical means (centroid) and the points it contains. Considering $\mu_m^u$ the centroid of the cluster $c_m^u$, KMeans minimizes the following objective function:

\begin{equation}
J(C_u)=\sum\limits_{m} \sum_{x^u_l\in c^u_m} \vert \vert x_l^u - \mu_m^u \vert \vert^2
\end{equation}

At the end, each scene $s_u$ is described by a set of clusters $C_u$. One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, which clusters not over a single scene, but over the whole dataset, and re-projects each scene in the resulting enhanced feature space. \ja{This sentence is also a big unclear.}

Here, with the aim of better balancing the influence of salient sound events and texture-like sounds on the final decision, the similarity between two scenes is computed based on their centroids similarities.

The similarity between all the scene centroids $\mu_i$, $i=[1,2,\ldots,I]$ with $I=UM$, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{ij} = \exp\left( - \dfrac{\Vert \mu_i - \mu_j \Vert^2}{\Vert \mu_i - \mu_{k,i} \Vert \Vert \mu_j - \mu_{k,j} \Vert} \right) 
\end{equation}

where $\mu_{k,i}$ and $\mu_{k,j}$ are the $k^{\textrm{th}}$ nearest neighbor to the centroids $\mu_i$ and $\mu_j$ respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

To compute the similarity between two scenes, we then consider several centroid-based similarity metrics:

\begin{itemize}
\item \emph{ob-closest} (ob-c): the similarity between two scenes is equal to the largest similarity between their centroids,
\item \emph{ob-averaged} (ob-a): the similarity between two scenes is equal to the average of their centroids similarities, and
\item \emph{ob-weighted} (ob-w): for each scene, each centroid is weighted according to the number of frames belonging to its cluster. Each scene $s_u$ is thus described by a signature $p_u$ of $M$ clusters ($p_u=\lbrace(\mu_1^u,w_1^u),(\mu_2^u,w_2^u),\ldots,(\mu_M^u,w_M^u)\rbrace$), with $\mu_m^u$ and $w_m^u$ being the centroid and the weight of the $m$th cluster respectively. A cross-bin histogram distance, taking into account both the clusters weights of the scenes and the distances between their cluster centroids is then used. 
\end{itemize}

For \emph{ob-w}, the cross-bin histogram distance used is a variant of the earth mover's distance ($\EMD$), known as $\widehat{\EMD}$ and introduced in \cite{pele2008linear}. $\EMD$ computes the distance between two histograms by finding the minimal cost to be paid to transform one histogram into the other. An advantage of $\EMD$ is that it automatically aligns the histogram bins by using a ``ground distance'' which is the distance between the bin centers in the two histograms. In our case, the histograms are the cluster weights $w^u$ defined over the bins formed by cluster centroids $\mu^u$.

The $\widehat{\EMD}$ variant of $\EMD$ is adapted for non-normalized histograms. To compute the $\widehat{\EMD}$, we use the implementation proposed in \cite{pele2009fast}. Given two signatures $p_u$ and $p_v$ made of $n$ and $m$ clusters respectively, the $\widehat{EMD}$ is computed by solving the following linear programming problem:

\begin{equation}
\begin{split}
\widehat{\EMD}(p_u,p_v) &=\left( \min\limits_{\lbrace f_{nm}\rbrace} \sum\limits_{n,m} f_{nm}D_{nm}^{uv} \right) \\
&+ \left|\sum\limits_{n} w_n^u - \sum\limits_{m} w_m^v  \right| \alpha \max\limits_{n,m}\lbrace  D_{nm}^{uv}\rbrace
\end{split}
\end{equation}

\begin{equation*}
\mathrm{s.t.} \quad f_{nm}\geq0 \quad \sum\limits_{m} f_{nm} \leq w_n^u \quad \sum\limits_{n} f_{nm} \leq w_m^v
\end{equation*}

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} \ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n$th bin to ``supply the demand'' of the $m$th bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroid sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=1-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$ respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

To get the final similarity measure between the scenes $s_u$ and $s_v$, an extended Gaussian kernels $K^s$ \cite{chapelle1999support,jing2003support} is computed:
\begin{equation}
\label{eq:ks}
K_{uv}^s = \exp\left( - \dfrac{\widehat{\EMD}(p_u,p_v)}{A} \right) \\
\end{equation}
with $A$ a scaling parameter, set to the mean value of the $\widehat{\EMD}$ between all the scenes. The resulting kernel $K^s$ is known as an EMD kernel, and it should be noted that there is no guarantee that this kernel is positive definite.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.
See text for details}
\end{center}
\ref{fig:folds}
\end{figure}
